A Constraint Solving Approach to Parikh Images of Regular Languages

### 2023-05-25 introduction.tex
Add new examples

\iffalse
It appears naturally as part of \Fudge{many operations} in model
checking and solving string constraints in automata-based solvers such
as \Ostrich{} \cite{ostrich}, notably in representing constraints on
string lengths. The enhanced \OstrichPlus{} solver~\cite{ostrich-plus}
makes even more extensive use of Parikh images.
\fi

@@

\iffalse
Later improvements have produced a construction taking at
most linear time to produce~\cite{muscholl-linear}. However, the
resulting existentially quantified clauses are costly to eliminate as
the number of variables increases, in practice making many real-world
problems intractable.
\fi

@@

>>>>

@@

@@

\subsection{An intuition for our method}

\begin{example}\label{ex:string-constraints}
    Consider the following set of string constraints:
\begin{constraints}
    \item\label{const:x-in-c-dd} $x \in \Regex{c\RegexOr{}dd}$
    \item\label{const:y-in-b} $y \in \Language(B)$, the language accepted by automaton~$B$ of \cref{fig:aut_b}.
    \item\label{const:x-substring} $x = \Substring(y, l, r)$
    \item\label{const:more-a-than-b} $\CountOf{\Char{a}}(y) > \CountOf{\Char{b}}(y)$, that is $y$ contains more letters \Char{a} than letters \Char{b}.
\end{constraints}
\end{example}

\cref{const:x-in-c-dd,const:y-in-b,const:x-substring} can be translated to the product of Parikh automata $B \times A'$, where $A'$ (\cref{fig:aut_a}) is the Parikh automata obtained by applying the encoding of $\Substring$ described in \cite{ostrich-plus}. Here follows an intuition for our method on $B \times A'$ under the global constraint \cref{const:more-a-than-b}. Note that the cost registers of \cref{fig:aut_b} are simply counting letters.

Each transition is associated with a fresh variable detailing how many times it is used

Counters are the sum of their increments times number of times the transition was used

TODO: rewrite the input and log it through CATRA!

\begin{figure}[h]
    \centering 
\begin{subfigure}[b]{0.49\textwidth}
    \centering
    \includegraphics[scale=\autscale]{b}
    \caption{The automaton $B$, where the Parikh registers count the number of occurrences of each letter.}\label{fig:aut_b}
      %\Description[SHORT]{LONG}
  \end{subfigure}

  \begin{subfigure}[b]{0.49\textwidth}
    \centering
    \includegraphics[scale=\autscale]{a}
    \caption{The automaton $A'$, whose Parikh registers count both the number of letters and the start ($l$) and length ($r$) of the substring.}\label{fig:aut_a}
      %\Description[SHORT]{LONG}
  \end{subfigure}
\end{figure}s
